\framework: Morphology-based Entity and Relational Entity Extraction Framework for Arabic

### 2018-03-17 tex/merf/TALMajor/methodology.tex
intro subsection moved to related work, edited methodology

For each MRE, 
\framework generates its equivalent non-deterministic finite automaton (NFA) in the typical manner~\cite{sipser2006introduction}. 
%Each MRE operation has its equivalent representation in an NFA. 
We support the upto operation ($f$\^{}$x$), which is not directly 
supported in ~\cite{sipser2006introduction}, by 
%it is equivalent to $f?|ff|\dots|\underbrace{f}_{x \text{ times}}$ which has an NFA mapping. 
%we can expand it into a standard regular expression form, for example
expanding it into a regular expression form; for example 
$f$\^{}$3$ is equivalent to $f?|ff|fff$. 
Consider the example of Figure~\ref{fig:intromotiv} and the
corresponding expression $(P|N)\!+~O?~R~O^\wedge 2~(P|N|U)+$. 
Figure~\ref{fig:nfaEx} shows part of the corresponding NFA where
$q_8, q_9, \dots, q_{13}$ represent NFA states,
and edges are transitions based on MBF tags such as 
$P,$ and $N$.
Edges labeled with the empty string $\epsilon$ are non-deterministic.
%The expression uses operations $|$, $?$, $+$, and $\wedge$ to relate places {\tt P}, names of persons {\tt N}, relative positions {\tt R}, numerical terms {\tt U}, and other {\tt O}.

\framework simulates the generated NFA over the sequence of tag sets matching the MBF formulae.
A simulation match $m$ of an expression $f$ is a tree where the root is the 
MRE expression, the internal nodes are the MRE and MBF operations, and the 
leaves are matches of the MAT terms of $f$.
The leave matches form a vector of tags
$\langle r_k,r_{k+1},\dots,r_j\rangle$ 
corresponding to the text sequence 
$\langle t_k,t_{k+1},\dots,t_j\rangle$ where $r_{\ell}\in R_{\ell},0\le k\le \ell \le j < n$.
%
%If the simulation has a match $\langle r_m,r_{m+1},\dots,r_n\rangle$ 
%where $0\le m\le n$, 
%the next simulation starts at $R_{n+1}$. 
%This disallows overlap of matches for the same MRE. 
%
%In case the NFA simulation has no match, 
%the next simulation starts at $R_{m+1}$. 
If we have more than one match %starting at $R_k$ where $0\le k\le n$, 
\framework returns the longest. 
%
Figure~\ref{fig:motiv}(b) shows two match trees of $\mathit{dir}$ extracted 
from the text of Figure~\ref{fig:intromotiv}.
\RL{dby} and \RL{mwl} are leaf nodes referring to name of place tags ($P$). 
The $+$, $|$, and $?$ MRE operations
are internal nodes.

@@

\framework computes the relational entities in a user defined 
relation $R=\ldbrack \langle e_1,e_2,r\rangle \rdbrack$
$\subseteq \ldbrack e_1 \rdbrack \times \ldbrack e_2 \rdbrack \times \ldbrack r \rdbrack$ 
to be the elements of $\ldbrack e_1 \rdbrack \times \ldbrack e_2 \rdbrack \times \ldbrack r \rdbrack$
with the smallest nonzero positive distance between the source and the destination
where the distance is the number of words between the matches.

%\framework supports the following configurations for the subexpressions of $e_i$ and $e_j$:
%\begin{itemize}
%\item $\left\vert{e_i}\right\vert=1\wedge\left\vert{e_j}\right\vert=1$: Relate $e_i$ match to $e_j$ match with edge labelled by $r$.
%\item $i=j\wedge\left\vert{e_i}\right\vert>1$: Relate sequences of $e_i$ matches with edges labelled by $r$.
%\item $i\neq j\wedge\left\vert{e_i}\right\vert>1\wedge\left\vert{e_j}\right\vert=1$: Relate each $e_i$ match to the single $e_j$ match with an edge labelled by $r$. The reverse applies for $\left\vert{e_i}\right\vert=1\wedge\left\vert{e_j}\right\vert>1$.
%\item $i\neq j\wedge\left\vert{e_i}\right\vert>1\wedge\left\vert{e_j}\right\vert>1$: Relate each $e_i$ match to each $e_j$ match with an edge labelled by $r$.
%\end{itemize}
%
In Figure~\ref{fig:motiv}(b), \framework names the subexpressions 
$(P|N)+$, $(P|N|U)+$, $O?$, $O\wedge 2$, and $R$, 
as $e_1, e_2, o_1, o_2,$ and $r$, respectively. 
The user defines the semantic relations
$\langle e_1, e_2, r\rangle$, 
$\langle r, e_1, o_1\rangle$, and 
$\langle r,e_2,o_2\rangle$.

The matches of $e_1,~e_2,~o_1,~o_2,$ and $r$ from the second match tree 
of Figure~\ref{fig:motiv}(b) are \RL{dby mwl}(Dubai Mall), 
\RL{Almbn_A}(the building), \RL{`l_A}(prep), \RL{mn h_dA}(from this), 
and \RL{mqrbT}(near), respectively. 
\framework~constructs the semantic relation matches and builds the lower part of the 
entity-relation graph shown in Figure~\ref{fig:intromotiv}.

For the first match \RL{brj _hlyfT bAlqrb mn AltqA.t` Al-'-wl},
the matches of $e_1,~e_2,~o_2,$ and $r$ are 
\RL{brj _hlyfT}(Khalifa tower), \RL{AltqA.t` Al-'-wl}(intersection 1), 
\RL{mn}(from), and \RL{bAlqrb}(next to), respectively. 
\framework~doesn't construct the relation $\langle r, e_1, o_1\rangle$ 
since $o_1$ has no match. 
Therefore, we get the upper part of the entity-relation graph shown 
in Figure~\ref{fig:intromotiv}.

After computing the relational entities, 
\framework~computes a cross-reference relation between the extracted entities
using a second order synonymy feature ($Syn^2$).
The \cci{isA} edge in the 
graph of Figure~\ref{fig:intromotiv} shows the cross-reference relation 
between \RL{brj _hlyfT}(Khalifa tower) from the first match 
with \RL{Almbn_A}(the building) from the second match.

>>>>

For each MRE, 
\framework generates its equivalent non-deterministic finite automaton (NFA) in the typical manner~\cite{sipser2006introduction}.
%Each MRE operation has its equivalent representation in an NFA. 
We support the upto operation ($f$\^{}$x$), which is not directly 
supported in~\cite{sipser2006introduction}, by 
%it is equivalent to $f?|ff|\dots|\underbrace{f}_{x \text{ times}}$ which has an NFA mapping. 
%we can expand it into a standard regular expression form, for example
expanding it into a regular expression form; for example 
$f$\^{}$3$ is equivalent to $f?|ff|fff$. 
Consider the example of Figure~\ref{fig:intromotiv} and the
corresponding expression $(P|N)\!+~O?~R~O^\wedge 2~(P|N|U)+$. 
Figure~\ref{fig:nfaEx} shows part of the corresponding NFA where
$q_8, q_9, \dots, q_{13}$ represent NFA states,
and edges are transitions based on MBF tags such as 
$P,$ and $N$.
Edges labeled with the empty string $\epsilon$ are non-deterministic.
%The expression uses operations $|$, $?$, $+$, and $\wedge$ to relate places {\tt P}, names of persons {\tt N}, relative positions {\tt R}, numerical terms {\tt U}, and other {\tt O}.

\framework simulates the generated NFA over the sequence of tag sets matching the MBF formulae.
%A simulation match $m$ of an expression $f$ is a tree where the root is the MRE expression, the internal nodes are the MRE and MBF operations, and the leaves are matches of the MAT terms of $f$.
A simulation match $m$ of an expression $f$ is a tree where the root spans the expression, the internal nodes are roots to sub-expressions of $f$, and the leaves are matches of the MBF formulae of $f$, e.g. Fig.~\ref{fig:taskMRE}.
The sequence of leaf matches forms a vector of tags $\langle r_k,r_{k+1},\dots,r_j\rangle$ 
corresponding to the text sequence 
$\langle t_k,t_{k+1},\dots,t_j\rangle$ where $r_{\ell}\in R_{\ell},0\le k\le \ell \le j < n$.
%
%If the simulation has a match $\langle r_m,r_{m+1},\dots,r_n\rangle$ 
%where $0\le m\le n$, 
%the next simulation starts at $R_{n+1}$. 
%This disallows overlap of matches for the same MRE. 
%
%In case the NFA simulation has no match, 
%the next simulation starts at $R_{m+1}$. 
If we have more than one match for an expression, 
%starting at $R_k$ where $0\le k\le n$, 
\framework returns the longest.
%Figure~\ref{fig:taskMRE} shows two match trees of $\mathit{dir}$ extracted from the text of Figure~\ref{fig:intromotiv}.
%\RL{dby} and \RL{mwl} are leaf nodes referring to name of place tags ($P$).
%The $+$, $|$, and $?$ MRE operations are internal nodes.

@@

Next, \framework computes the relational entities corresponding to each user defined relation $\ldbrack \langle e_1,e_2,r\rangle \rdbrack$
$\subseteq \ldbrack e_1 \rdbrack \times \ldbrack e_2 \rdbrack \times \ldbrack r \rdbrack$.
Note that the number of matches for $e_i$ ($\ldbrack e_i \rdbrack$) depends on the corresponding sub-expression.
For instance, we could have multiple matches if we associate $e_i$ with the sub-expression $P|N$ while we have $(P|N)+$.
%to be the elements of $\ldbrack e_1 \rdbrack \times \ldbrack e_2 \rdbrack \times \ldbrack r \rdbrack$
%with the smallest nonzero positive distance between the source and the destination
%where the distance is the number of words between the matches. 
Hence, \framework supports the following configurations for $e_i$ and $e_j$ based on the corresponding matches of sub-expressions:
\begin{itemize}
\item $\left\vert{e_i}\right\vert=1\wedge\left\vert{e_j}\right\vert=1$: Relate $e_i$ match to $e_j$ match with edge labeled by $r$.
\item $i=j\wedge\left\vert{e_i}\right\vert>1$: Relate sequences of $e_i$ matches with edges labeled by $r$.
\item $i\neq j\wedge\left\vert{e_i}\right\vert>1\wedge\left\vert{e_j}\right\vert=1$: Relate each $e_i$ match to the single $e_j$ match with an edge labeled by $r$. The reverse applies for $\left\vert{e_i}\right\vert=1\wedge\left\vert{e_j}\right\vert>1$.
\item $i\neq j\wedge\left\vert{e_i}\right\vert>1\wedge\left\vert{e_j}\right\vert>1$: Relate each $e_i$ match to each $e_j$ match with an edge labeled by $r$.
\end{itemize}

%In Figure~\ref{fig:taskMRE}, \framework names the sub-expressions $(P|N)+$, $(P|N|U)+$, $O?$, $O\wedge 2$, and $R$, as $e_1, e_2, o_1, o_2,$ and $r$, respectively. 
%The user defines the semantic relations $\langle e_1, e_2, r\rangle$, $\langle r, e_1, o_1\rangle$, and $\langle r,e_2,o_2\rangle$.

%The matches of $e_1,~e_2,~o_1,~o_2,$ and $r$ from the second match tree of Figure~\ref{fig:motiv}(b) are \RL{dby mwl}(Dubai Mall), \RL{Almbn_A}(the building), \RL{`l_A}(prep), \RL{mn h_dA}(from this), and \RL{mqrbT}(near), respectively. 
%\framework~constructs the semantic relation matches and builds the lower part of the entity-relation graph shown in Figure~\ref{fig:intromotiv}.

%For the first match \RL{brj _hlyfT bAlqrb mn AltqA.t` Al-'-wl}, the matches of $e_1,~e_2,~o_2,$ and $r$ are \RL{brj _hlyfT}(Khalifa tower), \RL{AltqA.t` Al-'-wl}(intersection 1), \RL{mn}(from), and \RL{bAlqrb}(next to), respectively. 
%\framework doesn't construct the relation $\langle r, e_1, o_1\rangle$ since $o_1$ has no match. 
%Therefore, we get the upper part of the entity-relation graph shown in Figure~\ref{fig:intromotiv}.

After computing the relational entities, 
\framework computes cross-reference relations between the extracted entities using a second order synonymy feature ($Syn^2$).
%The \cci{isA} edge in the graph of Figure~\ref{fig:intromotiv} shows the cross-reference relation between \RL{brj _hlyfT}(Khalifa tower) from the first match with \RL{Almbn_A}(the building) from the second match.

### 2018-03-17 tex/merf/TALMajor/relatedwork.tex
In progress: New methodology section ...
intro subsection moved to related work, edited methodology

@@

{\bf Information Extraction.~}
The common pattern specification language (CPSL) targets system independent 
IE specifications. 
CPSL consists of 
(1) a declaration part specifying names and labels, 
(2) a rule definition part specifying patterns, regular expressions and associated actions, and 
(3) and macro text substitution part~\cite{appelt1998common}.
\framework extends CPSL with Arabic morphological features, code actions, and user defined relations.

SystemT~\cite{chiticariu2010systemt}
aims to overcome the performance and expressivity limitations of CPSL.
It is based on an algebraic approach to declarative information extraction,
uses the declarative annotation query language (AQL), and uses
an optimizer to generate high performance execution plans for the AQL rules. 
%The AQL query is translated into an algebraic expression and an optimizer selects an execution plan. 
%\framework overcomes the limitations described by SystemT. 
\framework supports multiple tags per word, and supports the MRE conjunction operator
which allows for overcoming the overlapping annotation problem. 
%es the overfor each word and this overcomes the lossy sequencing caused 
%by random annotation dropping. 
%\framework introduces the conjunction operation in the MRE to overcome the expressivity limitations of expressing rules with overlapping annotations.

The work in~\cite{urbain2012user} presents a user 
driven relational model and targets entity and relation extraction. 
The user enters a natural language query, and uses the OpenNLP toolkit to 
extract tags and relations from the query. 
Then it extends the extracted entities into a query model,
and uses the query model to extract matches from the document. 
Similar to \framework, the system constructs entities and relations.

@@

DUALIST is an annotation system for quickly building classifiers for 
text processing tasks using active learning and semi-supervised learning~\cite{settles2011closing}. 
The classifier is interactive as it queries the annotator 
for entity detetction correction and annotation correction. 
\framework doesn't support classification tasks. 
However, \framework provides an interactive GUI where the user can edit MBF and MRE tags. 
This interactive environment contributes to the regular expression 
extraction and semantic relation construction which increases the overall accuracy.

WordNet is a lexical reference system that mimics human lexical memory 
%inspired by psycholinguistic theories 
and that relates words based on their semantic values and their functional 
categories: nouns, verbs, adjectives, adverbs, and function words~\cite{intro}. 
The $Syn^k$ feature in \framework is inspired by WordNet.

{\bf Annotation tools.~}
An overview of annotation tools and their Arabic-English word alignment issues 
concludes with a set of rules and guidelines needed in an Arabic annotation alignment tool
~\cite{kholidy2010towards}. 
The work in \cite{dukes2011supervised} presents a collaborative effort towards morphological 
and syntactic annotation of the Quran. 
\cite{dorr2010interlingual} presents a framework for interlingual 
annotation of parallel text corpora with multi-level representations. 
\cite{kulick2010consistent} presents the integration of the 
Standard Arabic Morphological Analyzer (SAMA) into the workflow of the Arabic Treebank.

MMAX2 is a manual multi-level linguistic annotation tool with an XML 
based data model~\cite{mmax2}. 
It enables the user to create, browse, visualize, and query annotations
and may be able to resolve coreference tags. 
BRAT~\cite{brat} and WordFreak~\cite{wordfreak} are manual 
multi-lingual user friendly web-based annotators that allow the construction 
of entity and relation annotation corpora~\cite{brat}. 
They can be extended through plug-ins to enable automatic annotators 
and customized annotation visualization specifications.
Knowtator~\cite{ogren2006knowtator} is a general purpose incremental text annotation tool 
implemented as a Prot\'eg\'e~\cite{gennari2003evolution} plug-in. 
Prot\'eg\'e is an open-source platform with a suite of tools to construct domain 
models and knowledge-based applications with ontologies. 
However, it doesn't support the Arabic language.

@@

@@

Task specific annotation tools such as~\cite{alrahabi2006semantic}
uses enunciation semantic maps to automatically annotate 
directly reported Arabic and French speech. 
AraTation is another task specific tool for semantic annotation of 
Arabic news using web ontology based semantic maps~\cite{saleh2009aratation}.
We differ in that \framework is general, and not task specific, and it uses 
morphology-based features as atomic terms.
Fassieh is a commercial Arabic text annotation tool that enables the production of large 
Arabic text corpora~\cite{attia2009fassieh}. 
The tool supports Arabic text factorization including morphological analysis, POS tagging, 
full phonetic transcription, and lexical semantics analysis in an automatic mode. 
Fassieh is not directly accessible to the research community and requires commercial licensing. 
\framework is open source and differs in that it allows the user to build tag types 
and extract entities and relations from text.

@@

Knowledge-based techniques such 
as~\cite{zaghouani2010adapting,traboulsi2009arabic} propose local grammars 
with morphological stemming to perform NER. 
%The work in~
\cite{ZaMaHaCicling2012Entity} presents a method for extracting entities, 
events, and relations amongst them from Arabic text using a hierarchy of manually built 
finite state machines driven by morphological features and graph 
transformation algorithms. 
Such techniques require advanced linguistic and programming expertise. 
QARAB is a question answering system that takes 
Arabic natural language queries and provides short answers~\cite{hammo2002qarab}.

>>>>

{\bf Information Extraction.~}
The common pattern specification language (CPSL) targets system independent IE specifications. 
CPSL consists of 
(1) a declaration part specifying names and labels, 
(2) a rule definition part specifying patterns, regular expressions and associated actions, and 
(3) macro text substitution part~\cite{appelt1998common}.
\framework extends CPSL with Arabic morphological features, code actions, and user defined relations.

SystemT~\cite{chiticariu2010systemt}
aims to overcome the performance and expressivity limitations of CPSL.
It is based on an algebraic approach to declarative information extraction, 
uses the declarative annotation query language (AQL), 
and uses an optimizer to generate high performance execution plans for the AQL rules.
%The AQL query is translated into an algebraic expression and an optimizer selects an execution plan. 
%\framework overcomes the limitations described by SystemT. 
\framework supports multiple tags per word, and supports the MRE conjunction operator which overcomes the overlapping annotation problem discussed in SystemT.
%es the overfor each word and this overcomes the lossy sequencing caused 
%by random annotation dropping. 
%\framework introduces the conjunction operation in the MRE to overcome the expressivity limitations of expressing rules with overlapping annotations.

The work in~\cite{urbain2012user} presents a user 
driven relational model and targets entity and relation extraction. 
The user enters a natural language query, and uses the OpenNLP toolkit to 
extract tags and relations from the query. 
Then, it extends the extracted entities into a query model,
and uses the query model to extract matches from the document. 
Similar to \framework, the system constructs entities and relations.

@@

@@

DUALIST is an annotation system for quickly building classifiers for 
text processing tasks using active learning and semi-supervised learning~\cite{settles2011closing}. 
%The classifier is interactive as it queries the annotator for entity detection correction and annotation correction.
\framework doesn't support classification tasks. 
However, \framework provides an interactive GUI where the user can edit MBF and MRE tags.
This interactive environment contributes to the regular expression extraction 
and semantic relation construction which increases the overall accuracy.

Another track in the literature targets specific tasks such as NER using statistical machine learning techniques \cite{ekbal2010named,abdelrahman2010integrated}.
%The work in~\cite{ekbal2010named} presents a language independent approach for NER extraction using {\em support vector machines}. 
%The work in~\cite{abdelrahman2010integrated} integrates a semi-supervised bootstrapping pattern recognition technique, and a supervised classifier based on {\em conditional random fields} to solve NER problems.
Knowledge-based techniques such 
as~\cite{zaghouani2010adapting,traboulsi2009arabic} propose local grammars 
with morphological stemming to perform NER. 
%The work in~
\cite{ZaMaHaCicling2012Entity} presents a method for extracting entities and events, and relations amongst them from Arabic text using a hierarchy of manually built 
finite state machines driven by morphological features 
and graph transformation algorithms. 
Such techniques require advanced linguistic and programming expertise.

WordNet is a lexical reference system that mimics human lexical memory 
%inspired by psycholinguistic theories 
and relates words based on their semantic values and their functional 
categories: nouns, verbs, adjectives, adverbs, and function words~\cite{intro}.
The $Syn^k$ feature in \framework is inspired by WordNet.

{\bf Annotation tools.~}
MMAX2 is a manual multi-level linguistic annotation tool with an XML 
based data model~\cite{mmax2}.
%It enables the user to create, browse, visualize, and query annotations and may be able to resolve coreference tags. 
BRAT~\cite{brat} and WordFreak~\cite{wordfreak} are manual 
multi-lingual user friendly web-based annotators that allow the construction 
of entity and relation annotation corpora.
%They can be extended through plug-ins to enable automatic annotators and customized annotation visualization specifications.
Knowtator~\cite{ogren2006knowtator} is a general purpose incremental text annotation tool 
implemented as a Prot\'eg\'e~\cite{gennari2003evolution} plug-in. 
Prot\'eg\'e is an open-source platform with a suite of tools to construct domain models and knowledge-based applications with ontologies. 
However, it doesn't support the Arabic language.

@@

\cite{kholidy2010towards} present an overview of annotation tools 
%and their Arabic-English word alignment issues 
and concludes with a set of rules and guidelines needed in an Arabic annotation alignment tool.
The work in \cite{dukes2011supervised} presents a collaborative effort towards morphological and syntactic annotation of the Quran.
\cite{dorr2010interlingual} presents a framework for inter-lingual 
annotation of parallel text corpora with multi-level representations.
\cite{kulick2010consistent} presents the integration of the 
Standard Arabic Morphological Analyzer (SAMA) into the workflow of the Arabic Treebank.

@@

Task specific annotation tools such as~\cite{alrahabi2006semantic}
use enunciation semantic maps to automatically annotate 
directly reported Arabic and French speech.
AraTation is another task specific tool for semantic annotation of 
Arabic news using web ontology based semantic maps~\cite{saleh2009aratation}.
We differ in that \framework is general, and not task specific, and it uses 
morphology-based features as atomic terms.
Fassieh is a commercial Arabic text annotation tool that enables the production of large Arabic text corpora~\cite{attia2009fassieh}.
The tool supports Arabic text factorization including morphological analysis, POS tagging, 
full phonetic transcription, and lexical semantics analysis in an automatic mode.
Fassieh is not directly accessible to the research community and requires commercial licensing.
\framework is open source and differs in that it allows the user to build tag types and extract entities and relations from text.

@@

Knowledge-based techniques such 
as~\cite{zaghouani2010adapting,traboulsi2009arabic} propose local grammars 
with morphological stemming to perform NER. 
%The work in~
\cite{ZaMaHaCicling2012Entity} presents a method for extracting entities, 
events, and relations amongst them from Arabic text using a hierarchy of manually built 
finite state machines driven by morphological features and graph 
transformation algorithms. 
Such techniques require advanced linguistic and programming expertise.

QARAB is a question answering system that takes 
Arabic natural language queries and provides short answers~\cite{hammo2002qarab}.

### 2018-03-17 tex/merf/TALMajor/tool.tex
intro subsection moved to related work, edited methodology

A relation $R$ is defined by the user as a tuple 
$\langle e_1,e_2,r\rangle$ where 
$e_1,e_2,$ and $r$ are identifiers associated with 
sub-expressions of an expression $f$.
Matches of $R$ are a set of labeled binary edges
where matches of $e_1$ and $e_2$ are the source and destination nodes
and matches of $r$ are the edge labels.
We denote $\ldbrack \langle e_1,e_2,r\rangle \rdbrack$ to be the set of matches of $R$, and refer to them as user defined relational entities.

We are interested in constructing the relational entity graph in Figure~\ref{fig:intromotiv}.
Let $e_1,o_1,r,o_2,$ and $e_2$ be identifiers to the sub-expressions 
$(P|N)+$,$O?$,$R$,$O\wedge 2$, and $(P|N|U)+$, respectively.
We select $(P|N)+$ to denote an entity as it captures a composite place name such as \cci{Khalifa tower}.
The matches to $e_1$, $r$, $o_2$, and $e_2$ in match 1 (Fig.~\ref{fig:taskMRE}) are \RL{brj _hlyfT} (Khalifa Tower), \RL{bAlqrb} (next), \RL{mn} (to), and \RL{AltqA.t` Al-'wl} (first intersection).
Note that there is no match to the optional $O$ formula in match 1.
Similarly, the matches to $e_1$, $o_1$, $r$, $o_2$, and $e_2$ in the second match tree are
\RL{dby mwl} (Dubai Mall), \RL{`l_A} (is located), \RL{mqrbT} (near), \RL{mn h_dA} (this), and \RL{Almbn_A} (building), respectively.

\cci{Relation($e_1$,$e_2$,$r$)} creates the 
edge labeled \cci{next to} between \cci{Khalifa tower} and 
\cci{intersection 1} nodes from match 1, and the 
edge labeled \cci{near} between \cci{Dubai Mall} and \cci{the building} nodes from match 2.
\cci{Relation($r$,$e_1$,$o_1$)} creates the edge labeled \cci{prep} 
between \cci{Dubai Mall} and \cci{near} nodes from match 2. 
\cci{Relation($r$,$e_2$,$o_2$)} creates the edge labeled \cci{from} 
between \cci{intersection 1} and \cci{next to} nodes in 
match 1, and the 
edge labeled \cci{from this} between \cci{near} and \cci{the building} 
nodes in match 2.

>>>>

A relation is defined by the user as a tuple 
$\langle e_1,e_2,r\rangle$ where 
$e_1,e_2,$ and $r$ are identifiers associated with 
sub-expressions of an expression $f$.
Matches of the relation are a set of labeled binary edges
where matches of $e_1$ and $e_2$ are the source and destination nodes
and matches of $r$ are the edge labels.
We denote $\ldbrack \langle e_1,e_2,r\rangle \rdbrack$ to be the set of matches of the corresponding relation, 
and we refer to them as relational entities.

We are interested in constructing the relational entity graph in Figure~\ref{fig:intromotiv}.
Let $e_1,o_1,r,o_2,$ and $e_2$ be identifiers to the sub-expressions 
$(P|N)+$,$O?$,$R$,$O\wedge 2$, and $(P|N|U)+$, respectively.
%We select $(P|N)+$ to denote an entity as it captures a composite place name such as \cci{Khalifa tower}.
We define the semantic relations $\langle e_1, e_2, r\rangle$, $\langle r, e_1, o_1\rangle$, and $\langle r,e_2,o_2\rangle$.
The matches to $e_1$, $r$, $o_2$, and $e_2$ in match 1 (Fig.~\ref{fig:taskMRE}) are \RL{brj _hlyfT} (Khalifa Tower), \RL{bAlqrb} (next), \RL{mn} (to), and \RL{AltqA.t` Al-'wl} (first intersection).
Note that there is no match to the optional $O$ formula in match 1.
Similarly, the matches to $e_1$, $o_1$, $r$, $o_2$, and $e_2$ in the second match tree are
\RL{dby mwl} (Dubai Mall), \RL{`l_A} (is located), \RL{mqrbT} (near), \RL{mn h_dA} (this), and \RL{Almbn_A} (building), respectively.

Relation $\langle e_1,e_2,r\rangle$ creates the 
edge labeled \cci{next to} between \cci{Khalifa tower} and 
\cci{intersection 1} nodes from match 1, and the 
edge labeled \cci{near} between \cci{Dubai Mall} and \cci{the building} nodes from match 2.
Relation $\langle r,e_1,o_1\rangle$ creates the edge labeled \cci{prep} 
between \cci{Dubai Mall} and \cci{near} nodes from match 2. 
Relation $\langle r,e_2,o_2\rangle$ creates the edge labeled \cci{from} 
between \cci{intersection 1} and \cci{next to} nodes in 
match 1, and the 
edge labeled \cci{from this} between \cci{near} and \cci{the building} 
nodes in match 2.
